---
title: "rFIA"
output: word_document
---
```{r warning = FALSE, message = FALSE}
library(rFIA)
```


## Download & Load Data
```{r warning = FALSE, message = FALSE}
#ct <- getFIA(states = 'CT', dir = 'C:/Users/user/Desktop/rFIA/data')
#db <- readFIA('C:/Users/user/Desktop/rFIA/data')

# Data load
data('fiaRI') ## subset of the FIA Database for Rhode Island
data('countiesRI') ## county boundaries of Rhode Island
```

- states로 원하는 주만 선택가능
- dir : 해당 위치에 data 저장

## clipFIA
- 특정연도, 특정 주 일부에서 estimates 산출
```{r warning = FALSE, message = FALSE}
riMR = clipFIA(fiaRI, mostRecent = TRUE)
riBT_MR = clipFIA(fiaRI, mask = countiesRI[1,], mostRecent = TRUE) # BRISTOL
```

- option
  - mostRecent(default TRUE) : reporting years가 가장 최신인 것만
  - mask : define the boundaries of spatial intersection
  
- output : FIADB tables (자세한 내용은 FIADB User Guide.pdf 참고)
  - COND
  - COND_DWM_CALC
  - INVASIVE_SUBPLOT_SPP
  - P2VEG_SUBP_STRUCTURE
  - PLOT
  - POP_ESTN_UNIT
  - POP_EVAL
  - POP_EVAL_GRP
  - POP_EVAL_TYP
  - POP_PLOT_STRATUM_ASSGN
  - POP_STRATUM
  - SEEDLING
  - SUBP_COND
  - SUBP_COND_CHNG_MTRX
  - SUBPLOT
  - SURVEY
  - TREE
  - TREE_GRM_BEGIN
  - TREE_GRM_COMPONENT
  - TREE_GRM_MIDPT

## tpa
- Estimate trees per acre & basal area per acre
```{r warning = FALSE, message = FALSE}
tpaRI <- tpa(riMR)
head(tpaRI)
```

- output
  - YEAR : reporting year
  - TPA : mean trees per acre
  - BAA : mean basal area per acre (sq.ft.)
  - TPA_PERC : mean proportion of trees falling within the domain of interest, with respect to trees per acre
  - BAA_PERC : mean proportion of trees falling within the domain of interest, with respect to basal area per acre
  - nPlots_TREE : number of non-zero plots used to compute tree and basal area estimates
  - nPlots_AREA : number of non-zero plots used to compute land area estimates

### tpa - group estimates by species
```{r warning = FALSE, message = FALSE}
tpaRI_species = tpa(riMR, bySpecies = T)
head(tpaRI_species)
```

- SPCD, COMMON_NAME, SCIENTIFIC_NAME : TREE table에 존재하는 변수들

### tpa - group estimates by size class
```{r warning = FALSE, message = FALSE}
tpaRI_sizeClass = tpa(riMR, bySizeClass = T)
head(tpaRI_sizeClass)
```

- size class : 2-inch intervals

### tpa - Group by species and size class, and plot the distribution
```{r warning = FALSE, message = FALSE}
tpaRI_spsc <- tpa(riMR, bySpecies = TRUE, bySizeClass = TRUE)
plotFIA(tpaRI_spsc, BAA, grp = COMMON_NAME, x = sizeClass,
        plot.title = 'Size-class distributions of BAA by species', 
        x.lab = 'Size Class (inches)', text.size = .75,
        n.max = 5) # Only the top 5 species
```

### tpa - 특정 조건의 나무, 특정 지역 등으로 산출하고싶을 때
```{r warning = FALSE, message = FALSE}
tpaRI_own <- tpa(riMR, 
                 grpBy = OWNGRPCD, # groupby owner classes
                 treeDomain = DIA > 12 & CCLCD %in% c(1,2), 
                 areaDomain = PHYSCLCD %in% c(20:29)) 
head(tpaRI_own)
```

### tpa - 특정 population boundaries에 대해서만
```{r warning = FALSE, message = FALSE}
tpaRI_counties <- tpa(riMR, polys = countiesRI, returnSpatial = TRUE)
head(tpaRI_counties)
```

- polys : specifies the polygons(zones)
- returnSpatial = T : return sf multipolygon object

```{r warning = FALSE, message = FALSE}
plotFIA(tpaRI_counties, BAA)
```


## area
- Estimates of total area (acreage)
```{r warning = FALSE, message = FALSE}
area(riMR)
area(riMR, byLandType=T) # grouped by land class
area(riMR, landType='forest', treeDomain = DIA > 20) # DBH 20 이상
```

- option
  - byLandType = T :  return estimates grouped by land type classes (timberland, non-timberland forest, non-forest, water)
  - landType : forest / non-forest / census water / non-census water / water / all

- output
  - YEAR : reporting year
  - AREA : estimate of total area within domain of interest(acres)
  - nPlots : number of non-zero plots used to compute area estimates

## areaChange
- Estimate land area change
```{r warning = FALSE, message = FALSE}
areaChange(riMR)
areaChange(riMR, byLandType=T) # grouped by land class
areaChange(riMR, landType='forest', treeDomain = DIA > 20) # DBH 20 이상
```

- PERC_CHNG : 연간 백분율 변화 추정치(%)
- AREA_CHNG : 연간 변화 추정치(acre)
- PREV_AREA : 총 토지 면적 추정치(acre)


## biomass
- Estimate tree biomass and carbon stocks
```{r warning = FALSE, message = FALSE}
biomass(riMR, landType='timber', treeType='gs')
biomass(riMR, landType='timber', treeType='gs', component = c('AG', 'FOLIAGE'))
biomass(riMR, landType='timber', treeType='gs', component = c('AG', 'FOLIAGE', byPlot = T))

riMR$COND$STAND_AGE = makeClasses(riMR$COND$STDAGE, interval=10)
head(biomass(riMR, grpBy = STAND_AGE), n=8) # groupby stand age
```

- output
  - BIO_ACRE : estimate of mean tree biomass per acre(short tons/acre)
  - CARB_ACRE : estimate of mean tree carbon per acre(short tons/acre)

- option
  - landType : forest / timber
  - treeType : all / live / dead / gs(growing-stock)
  - byPlot = T : returns estimates for individual plot locations instead of population estimates.
  - component
    - TOTAL : sum of all components
    - AG : sum of aboveground components, excluding foliage
    - FOLIAGE : sapling foliage + stems larger than 5 in dbh
    - TOP
    - BOLE
    - STUMP
    - SAPLING : 묘목
    - WDLD_SPP : woodland species

```{r warning = FALSE, message = FALSE}
ctSF = biomass(riMR, polys = countiesRI, returnSpatial=T)
plot(ctSF)
plotFIA(ctSF, BIO_ACRE) # plot of aboveground biomass per acre
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## carbon
- Estimate carbon stocks(metric tonnes) by IPCC forest carbon pools
```{r warning = FALSE, message = FALSE}
carbon(riMR)
head(carbon(riMR, byPlot=T), n=10)
carbon(riMR, byComponent=T)
head(carbon(riMR, grpBy = STAND_AGE), n=10)
```

- output
  - CARB_ACRE : estimate of mean total carbon per acre(metric tonnes/acre)
- option
  - byPool = T : aboveground live, belowground live, dead wood, litter, soil organic(p961 REF_POP_ATTRIBUTE)
  - byComponent = T : return estimates grouped by IPCC forest carbon components

```{r warning = FALSE, message = FALSE}
ctSF = carbon(riMR, polys = countiesRI, returnSpatial=T, byPool=F, totals=T) # totals = T return total population estimates
plot(ctSF)
plotFIA(ctSF, CARB_TOTAL)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## diversity
- estimate diversity
- Shannon's index : 한 집단 내의 데이터의 class가 얼마나 다양한지 나타내는 지표
- Shannon's equitability : 각 diversity 값을 최대 diversity 값으로 나눠 정규화한 것
```{r warning = FALSE, message = FALSE}
diversity(riMR, landType='forest', treeType='live')

riMR$COND$STAND_AGE = makeClasses(riMR$COND$STDAGE, interval=10)
head(diversity(riMR, grpBy = STAND_AGE), n=8)

head(diversity(riMR, landType = 'timber', treeType = 'gs', bySizeClass=T), n=8) # 2-inch intervals
```

- output
  - H_a : Shannon's Diversity Index, alpha (stand) level
  - H_b : Shannon's Diversity Index, beta (landscape) level
  - H_g : Shannon's Diversity Index, gamma (regional) level
  - Eh_a : Shannon's Equitability Index, alpha (stand) level
  - Eh_b : Shannon's Equitability Index, beta (landscape) level
  - Eh_g : Shannon's Equitability Index, gamma (regional) level
  - S_a : Species Richness, alpha (stand) level
  - S_b : Species Richness, beta (landscape) level
  - S_g : Species Richness, gamma (regional) level

```{r warning = FALSE, message = FALSE}
ctSF = diversity(riMR, polys = countiesRI, returnSpatial=T)
plot(ctSF)
plotFIA(ctSF, H_a)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## dwm
- Estimate volume, biomass, carbon stocks of down woody material(fuels)
```{r warning = FALSE, message = FALSE}
dwm(riMR)
dwm(riMR, grpBy=OWNGRPCD)
```

- output
  - VOL_ACRE : estimate of mean volume per acre of dwm(cu.ft/acre)
  - BIO_ACRE : estimate of mean biomass per acre of dwm(short tons/acre)
  - CARB_ACRE : estimate of mean carbon mass per acre of dwm(short tons/acre)
- option
  - tidy = T : return estimates grouped by fuel type

```{r warning = FALSE, message = FALSE}
dwmSF = dwm(riMR, polys = countiesRI, returnSpatial = T, tidy = F)
plot(dwmSF)
plotFIA(dwmSF, BIO_ACRE)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## findEVALID
- Find EVALIDs
- Lookup Evaluation IDs associated with reporting years & evaluation types
```{r warning = FALSE, message = FALSE}
findEVALID(riMR)
```
- output
  - 2-digit State code + 2-digit year code + 2-digit evaluation type code

## fsi
- Estimate the Forest Stability Index
- Estimate annual change in relative live tree density
- FSI : compare actual changes in tree density to those expected
```{r warning = FALSE, message = FALSE}
fsi(riMR)
```

- output
  - FSI : estimate of forest stability index(annual change in relative live tree density)
  - PERC_FSI : estimate of % forest stability index(% annual change in relative live tree density)
  - FSI_STATUS : decline / stable / expand
  - FSI_INT : width of 95% CI of mean FSI
  - PREV_RD : estimate of relative live tree density at initial measurement of all plots
  - CURR_RD : estimate of relative live tree density at final measurement of all plots
  - TPA_RATE : standardized estimate of annual change in TPA
  - BA_RATE : standardized estimate of annual change in BA

```{r warning = FALSE, message = FALSE}
results = fsi(riMR, scaleBy = FORTYPCD, returnBetas = T)
results$results # FSI estimates
results$betas # model coefficients
```

- option
  - scaleBy : variables from PLOT or COND tables (to use as 'random effects')
  - returnBetas = T : return estimated coefficients of maximum size-density models along with results

- output
  - grps : unique identifier associated with the group
  - alpha : posterior median of scaling factor that describes the maximum tree density at average tree basal area of one sq. ft.
  - rate : posterior median of negative exponent controlling the decay in maximum tree density with increasing average tree size
  - n : number of observations with the group with an approximately normal diameter distribution and no evidence of recent disturbance

## makeClasses
- Convert numeric variables to class intervals(factor)


## growMort
- Estimates of recruitment, natural mortality, harvest rates
```{r warning = FALSE, message = FALSE}
growMort(riMR)

riMR$COND$STAND_AGE = makeClasses(riMR$COND$STDAGE, interval=10)
growMort(riMR, grpBy = STAND_AGE)
```

- output
  - RECR_TPA : estimate of mean annual recruitment as trees per acre
  - MORT_TPA : estimate of mean annual mortality as trees per acre
  - REMV_TPA : estimate of mean annual removals (harvest) as trees per acre
  - RECR_PERC : estimate of mean percent of individuals subject to recruitment annually
  - MORT_PERC : estimate of mean percent of individuals subject to mortality annually
  - REMV_PERC : estimate of mean percent of individuals subject to removal (harvest) annually

```{r warning = FALSE, message = FALSE}
ctSF = growMort(riMR, polys=countiesRI, returnSpatial=T)
plot(ctSF)
plotFIA(ctSF, MORT_TPA)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## invasive
- Estimates of areal coverage of invasive species
```{r warning = FALSE, message = FALSE}
invasive(riMR)
invasive(riMR, grpBy=STAND_AGE)
```

- output
  - SYMBOL : unique species ID from NRCS Plant Reference Guide
  - COVER_PCT : estimate of percent areal coverage of the species
  - COVER_AREA : estimate of areal coverage of the species(acres)
  - nPlots_INV : number of non-zero plots used to compute invasive coverage estimates


## plotFIA
- non-spatial summaries -> time-series plots
- spatial summaries(class sf) -> choropleth maps(단계구분도)
```{r warning = FALSE, message = FALSE}
tpaRI = tpa(fiaRI, polys=countiesRI, returnSpatial = T)

plotFIA(tpaRI, y=TPA, legend.title='Abundance(TPA)')
plotFIA(tpaRI, y=TPA, legend.title='Abundance(TPA)', transform='sqrt')
```

- option
  - transform : transformations to apply to plotted variable y


```{r warning = FALSE, message = FALSE}
tpaMR = tpa(riMR, polys=countiesRI, returnSpatial = T)

plotFIA(tpaMR, y=TPA, legend.title='Abundance(TPA)')
```

```{r warning = FALSE, message = FALSE}
# no spatial grouping -> time series plot
tpaRI = tpa(fiaRI)

plotFIA(tpaRI, y=TPA)
```

```{r warning = FALSE, message = FALSE}
tpaRI_sc = tpa(riMR, bySpecies=T, bySizeClass=T)
plotFIA(tpaRI_sc, y=BAA, grp=COMMON_NAME, x=sizeClass, n.max=4)
```


## seedling
- Estimate seedling(< 1 inch DBH) abundance per acre
```{r warning = FALSE, message = FALSE}
seedling(riMR, landType='timber')
seedling(riMR, treeDomain = SPCD == 129, areaDomain = PHYSCLCD %in% 21:29)
```

- option
  - TPA : estimate of mean trees per acre
  - TPA_PERC : estimate of mean proportion of live trees falling within the domain of interest, with respect to trees per acre

## standStruct
- Estimate forest structural stage distribution
```{r warning = FALSE, message = FALSE}
standStruct(riMR)
standStruct(riMR, areaDomain=PHYSCLCD %in% c(11:19))
```

- output
  - STAGE : stand structural stage
  - PERC : % land area in each structural stage

- Structural Stage Classification
  - Pole : > 67% BA in pole and mature classes, with more BA in pole than mature
  - Mature : > 67% BA in pole and mature classes, with more BA in mature than pole OR
             > 67% BA in mature and large classes, with more BA in mature.
  - Late-Successional : > 67% BA in mature and large classes, with more in large
  - Mosaic : Any plot not meeting above criteria

```{r warning = FALSE, message = FALSE}
sdSF = standStruct(riMR, polys=countiesRI, returnSpatial=T, tidy=F)
plot(sdSF)
plotFIA(sdSF, POLE_PERC)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## vegStruct
- Estimate vegetation cover by canopy layer
```{r warning = FALSE, message = FALSE}
head(vegStruct(riMR), n=10)
```

- output
  - LAYER : canopy layer
  - GROWTH_HABIT : species growth habit
  - COVER_PCT : estimate of percent areal coverage of the growth habit within the canopy layer
  - COVER_AREA : estimate of areal coverage of the growth habit within the canopy layer(acres)
  - AREA : estimate of total land area (acres)
  - nPlots_VEG : number of non-zero plots used to compute areal coverage estimates

## vitalRates
- Estimate tree growth rates
```{r warning = FALSE, message = FALSE}
vitalRates(riMR, landType = 'timber', treeType = 'gs')
vitalRates(riMR, treeType = 'live', treeDomain = SPCD == 129 & DIA > 12, areaDomain = PHYSCLCD %in% 21:29)
head(vitalRates(riMR, landType = 'forest', bySpecies = T), n=10)
```
- output
  - DIA_GROW : diameter growth of a stem
  - BA_GROW : basal area growth of a stem
  - BAA_GROW : basal area growth per acre
  - NETVOL_GROW : net volume growth of a stem
  - NETVOL_GROW_AC : net volume growth per acre
  - SAWVOL_GROW : net sawlog volume growth of a stem
  - SAWVOL_GROW_AC : net sawlog volume growth per acre
  - BIO_GROW : aboveground biomass growth of a stem
  - BIO_GROW_AC : aboveground biomass growth per acre

```{r warning = FALSE, message = FALSE}
ctSF = vitalRates(riMR, polys = countiesRI, returnSpatial = T)
plot(ctSF)
plotFIA(ctSF, BIO_GROW)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑

## volume
- Estimate merchantable tree volume
```{r warning = FALSE, message = FALSE}
volume(riMR, landType = 'timber', treeType = 'gs')
volume(riMR, landType = 'timber', treeType = 'gs', volType = 'gross')

riMR$COND$STAND_AGE = makeClasses(riMR$COND$STDAGE, interval=10)
volume(riMR, grpBy = STAND_AGE)

head(volume(riMR, landType = 'forest', treeType = 'live', bySpecies = T), n=10)
```
- option
  - volType : NET / SOUND / GROSS
- output
  - BOLE_CF_ACRE : estimate of mean merchantable bole volume per acre (cu.ft./acre)
  - SAW_CF_ACRE : estimate of mean tree carbon per acre(thousand board)

```{r warning = FALSE, message = FALSE}
ctSF = volume(riMR, polys = countiesRI, returnSpatial = T)
plot(ctSF)
plotFIA(ctSF, SAW_MBF_ACRE)
```

- 노랑 > 주황 > 핑크 > 보라 > 파랑





